### Getting the data {.tabset}
Load the data gene expression data from Kallisto output and make a list object with various components. These data were obtained from multiple published sources. The goby and zebrafish data were generated for this study.  
I plot the PCA of the developmental time-series to show the variation across stages.
```{r 02_getting_data-chunk-001, cache=TRUE, cache.path="cache/02_getting_data/"}
#Grouper
expression_matrix_and_pca(sp = "Grouper",colramp = colorRampPalette(c("#4d3f2c","#aa9576","#D9AD22","#D9C343")))->grouper
#Manini
expression_matrix_and_pca(sp = "Manini",colramp = colorRampPalette(c("grey40","grey","#f7f2a9","#9acd32")))->manini
#Goby
expression_matrix_and_pca(sp = "Goby",colramp = colorRampPalette(c("#45BA99","#5E45BA","#BA4566","#A1BA45")))->goby
#Clown
expression_matrix_and_pca_clown()->clown
#Danio
expression_matrix_and_pca_danio()->danio
```

#### Clownfish
```{r 02_getting_data-chunk-002, cache=TRUE, cache.path="cache/02_getting_data/", out.width  = "70%"}
clown$plot
```

#### Manini
```{r 02_getting_data-chunk-003, cache=TRUE, cache.path="cache/02_getting_data/", out.width  = "70%"}
manini$plot
```

#### Goby
```{r 02_getting_data-chunk-004, cache=TRUE, cache.path="cache/02_getting_data/", out.width  = "70%"}
goby$plot
```

#### Grouper
```{r 02_getting_data-chunk-005, cache=TRUE, cache.path="cache/02_getting_data/", out.width  = "70%"}
grouper$plot
```

#### Zebrafish
```{r 02_getting_data-chunk-006, cache=TRUE, cache.path="cache/02_getting_data/", out.width  = "70%"}
danio$plot
```
