## Making the network {.tabset}

### Soft threshold
The first step is to estimate the power to achieve the scale free topology of the data. Choosing a soft threshold power for the developmental time-series data is not straight forward due to the dynamic nature of the gene expression. Therefore, I chose a power that balances the scale free nature of the data and it's mean connectivity to ensure that I don't get too sparse networks. I pick the highest power that has a mean connectivity of greater than 100.  
I do not load these networks as they were not used in the study. I keep this code here for completeness. 
```{r 03_making_network-chunk-001, eval=FALSE}
#Grouper
soft_threshold(grouper$wgcna_in)->sft_grouper#pick 14
#Manini
soft_threshold(manini$wgcna_in)->sft_manini #pick 13
#Goby
soft_threshold(goby$wgcna_in)->sft_goby #pick 10
#Clownfish
soft_threshold(clown$wgcna_in)->sft_clown#pick 11
#Danio
soft_threshold(danio$wgcna_in)->sft_danio#pick 11
```

### Network construction step
This step constructs the network.
```{r 03_making_network-chunk-002, eval=FALSE}
#Grouper
wgcna_adjacency(datExpr = grouper$wgcna_in, power = 14)->grouper_net
grouper_net %>% saveRDS("./02.Gene_expression_and_network/grouper_net.rds")

#Manini
wgcna_adjacency(datExpr = manini$wgcna_in, power = 13)->manini_net
manini_net %>% saveRDS("./02.Gene_expression_and_network/manini_net.rds")

#Goby
wgcna_adjacency(datExpr = goby$wgcna_in, power = 10)->goby_net
goby_net %>% saveRDS("./02.Gene_expression_and_network/goby_net.rds")

#Clown
wgcna_adjacency(datExpr = clown$wgcna_in, power = 11)->clown_net
clown_net %>% saveRDS("./02.Gene_expression_and_network/clown_net.rds")

#Danio
wgcna_adjacency(datExpr = danio$wgcna_in, power = 11)->danio_net
danio_net %>% saveRDS("./02.Gene_expression_and_network/danio_net.rds")

```

### Load networks
```{r 03_making_network-chunk-003, cache=TRUE, cache.path="cache/03_making_network/",eval=FALSE}
grouper_net<-readRDS("./02.Gene_expression_and_network/grouper_net.rds")
manini_net<-readRDS("./02.Gene_expression_and_network/manini_net.rds")
goby_net<-readRDS("./02.Gene_expression_and_network/goby_net.rds")
clown_net<-readRDS("./02.Gene_expression_and_network/clown_net.rds")
danio_net<-readRDS("./02.Gene_expression_and_network/danio_net_pruned.rds")
```
