## Finding homologous modules 

### Module preservation {.tabset}
To quantify similarities between the post-embryonic co-expression networks I estimated module preservation statistics, which measure how well network properties are conserved between a reference and a test network. I performed pairwise comparisons of the network properties among all species. Since the networks were constructed using a one-to-one orthologous gene expression matrix, the estimate of module preservation tells us whether gene interactions during post-embryonic development in one species resemble another species.  
The Zsummary score is used to denote the degree of preservation with scores above 10 typically used as evidence of high preservation and scores below 2 as evidence of no preservation. To get more reliable estimates I use more stringent thresholds to categorise preservation, with  Zsummary > 12 as evidence of high preservation, Zsummary  < 12 as evidence for low to medium preservation, and Zsummary  < 6 as no evidence for preservation. 
```{r 06_homologous_modules_and_gene_lists-chunk-001, eval=FALSE}
## Module preservation analysis
#In this step I check whether the co-expression modules identified in one species are preserved in another species. 

#For clownfish and grouper
setLabels = c("clown", "grouper");
multiExpr = list(clown = list(data = clown_orth_net_in$wgcna_in), 
                 grouper = list(data = grouper_orth_net_in$wgcna_in));
multiColor = list(clown = clown_orth_net$moduleColors$moduleColors, 
                  groper = grouper_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_grouper.rds")

#For clownfish and manini
setLabels = c("clown", "manini");
multiExpr = list(clown = list(data = clown_orth_net_in$wgcna_in), 
                 manini = list(data = manini_orth_net_in$wgcna_in));
multiColor = list(clown = clown_orth_net$moduleColors$moduleColors, 
                  manini = manini_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_manini.rds")

#For clownfish and goby
setLabels = c("clown", "goby");
multiExpr = list(clown = list(data = clown_orth_net_in$wgcna_in), 
                 goby = list(data = goby_orth_net_in$wgcna_in));
multiColor = list(clown = clown_orth_net$moduleColors$moduleColors, 
                  goby = goby_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_goby.rds")

#For clownfish and danio
setLabels = c("clown", "danio");
multiExpr = list(clown = list(data = clown_orth_net_in$wgcna_in), 
                 danio = list(data = danio_orth_net_in$wgcna_in));
multiColor = list(clown = clown_orth_net$moduleColors$moduleColors, 
                  danio = danio_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_danio.rds")

#For manini and grouper
setLabels = c("manini", "grouper");
multiExpr = list(manini = list(data = manini_orth_net_in$wgcna_in), 
                 grouper = list(data = grouper_orth_net_in$wgcna_in));
multiColor = list(manini = manini_orth_net$moduleColors$moduleColors, 
                  grouper = grouper_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_manini_grouper.rds")

#For manini and goby
setLabels = c("manini", "goby");
multiExpr = list(manini = list(data = manini_orth_net_in$wgcna_in), 
                 goby = list(data = goby_orth_net_in$wgcna_in));
multiColor = list(manini = manini_orth_net$moduleColors$moduleColors, 
                  goby = goby_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_manini_goby.rds")

#For manini and danio
setLabels = c("manini", "danio");
multiExpr = list(manini = list(data = manini_orth_net_in$wgcna_in), 
                 danio = list(data = danio_orth_net_in$wgcna_in));
multiColor = list(manini = manini_orth_net$moduleColors$moduleColors, 
                  danio = danio_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_manini_danio.rds")


#For goby and grouper
setLabels = c("goby", "grouper");
multiExpr = list(goby = list(data = goby_orth_net_in$wgcna_in), 
                 grouper = list(data = grouper_orth_net_in$wgcna_in));
multiColor = list(goby = goby_orth_net$moduleColors$moduleColors, 
                  groper = grouper_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_goby_grouper.rds")

#For goby and danio
setLabels = c("goby", "danio");
multiExpr = list(goby = list(data = goby_orth_net_in$wgcna_in), 
                 danio = list(data = danio_orth_net_in$wgcna_in));
multiColor = list(goby = goby_orth_net$moduleColors$moduleColors, 
                  groper = danio_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_goby_danio.rds")

#For grouper and danio
setLabels = c("grouper", "danio");
multiExpr = list(grouper = list(data = grouper_orth_net_in$wgcna_in), 
                 danio = list(data = danio_orth_net_in$wgcna_in));
multiColor = list(grouper = grouper_orth_net$moduleColors$moduleColors, 
                  danio = danio_orth_net$moduleColors$moduleColors);
nSets = 2

mp = modulePreservation(multiExpr, multiColor,
referenceNetworks = c(1:2),
nPermutations = 200,
randomSeed = 1,
verbose = 3)
mp %>% saveRDS("./02.Gene_expression_and_network/orth_module_pres_grouper_danio.rds")

```

#### Loading the module pres plots {.tabset}
These are individual module preservation plots between pair-wise speices comparisons. 
```{r 06_homologous_modules_and_gene_lists-chunk-002, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", message=FALSE, results='hide'}
#clownfish
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_grouper.rds"),
                  heatdat=clown_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.clown)->mp_plot_clown_ref_grouper
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_manini.rds"),
                  heatdat=clown_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.clown)->mp_plot_clown_ref_manini
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_goby.rds"),
                  heatdat=clown_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.clown)->mp_plot_clown_ref_goby
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_danio.rds"),
                  heatdat=clown_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.clown)->mp_plot_clown_ref_danio
#manini
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_manini.rds"),
                  heatdat=manini_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.manini)->mp_plot_manini_ref_clown

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_grouper.rds"),
                  heatdat=manini_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.manini)->mp_plot_manini_ref_grouper

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_goby.rds"),
                  heatdat=manini_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.manini)->mp_plot_manini_ref_goby

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_danio.rds"),
                  heatdat=manini_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.manini)->mp_plot_manini_ref_danio

#Grouper
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_grouper.rds"),
                  heatdat=grouper_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.grouper)->mp_plot_grouper_ref_clown

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_grouper.rds"),
                  heatdat=grouper_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.grouper)->mp_plot_grouper_ref_manini

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_goby_grouper.rds"),
                  heatdat=grouper_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.grouper)->mp_plot_grouper_ref_goby

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_grouper_danio.rds"),
                  heatdat=grouper_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.grouper)->mp_plot_grouper_ref_danio

#Goby
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_goby.rds"),
                  heatdat=goby_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.goby)->mp_plot_goby_ref_clown

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_goby.rds"),
                  heatdat=goby_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.goby)->mp_plot_goby_ref_manini

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_goby_grouper.rds"),
                  heatdat=goby_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.goby)->mp_plot_goby_ref_grouper

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_goby_danio.rds"),
                  heatdat=goby_orth_heatmap$dat, 
                  c1=1, c2=2, 
                  cols=cols.goby)->mp_plot_goby_ref_danio

#Danio
module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_clownfish_danio.rds"),
                  heatdat=danio_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.danio)->mp_plot_danio_ref_clown

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_manini_danio.rds"),
                  heatdat=danio_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.danio)->mp_plot_danio_ref_manini

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_grouper_danio.rds"),
                  heatdat=danio_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.danio)->mp_plot_danio_ref_grouper

module_pres_plots(mp=readRDS("./02.Gene_expression_and_network/orth_module_pres_goby_danio.rds"),
                  heatdat=danio_orth_heatmap$dat, 
                  c1=2, c2=1, 
                  cols=cols.danio)->mp_plot_danio_ref_goby


rbind(clown_orth_net$connectivity %>% mutate(species="clown"),manini_orth_net$connectivity %>% mutate(species="manini"),grouper_orth_net$connectivity %>% mutate(species="grouper"),goby_orth_net$connectivity %>% mutate(species="goby"),danio_orth_net$connectivity %>% mutate(species="danio"))->orth_assignments
```

##### Clownfish~Grouper
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_clown_ref_grouper
```

##### Clownfish~Manini
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_clown_ref_manini
```

##### Clownfish~Goby
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_clown_ref_goby
```

##### Clownfish~Danio
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_clown_ref_danio
```

##### Manini~Clownfish
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_manini_ref_clown
```

##### Manini~Grouper
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_manini_ref_grouper
```

##### Manini~Goby
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_manini_ref_goby
```

##### Manini~Danio
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_manini_ref_danio
```

##### Grouper~Clownfish
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_grouper_ref_clown
```

##### Grouper~Manini
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_grouper_ref_manini
```

##### Grouper~Goby
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_grouper_ref_goby
```

##### Grouper~Danio
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_grouper_ref_danio
```

##### Goby~Clownfish
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_goby_ref_clown
```

##### Goby~Manini
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_goby_ref_manini
```

##### Goby~Grouper
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_goby_ref_grouper
```

##### Goby~Danio
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_goby_ref_danio
```

##### Danio~Clownfish
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_danio_ref_clown
```

##### Danio~Manini
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_danio_ref_manini
```

##### Danio~Grouper
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_danio_ref_grouper
```

##### Danio~Goby
```{r, message=FALSE, fig.width=10, fig.height=3}
mp_plot_danio_ref_goby
```

### Degree of preservation {.tabset}
```{r 06_homologous_modules_and_gene_lists-chunk-003, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", fig.height=6, fig.width=10}
rbind(
mp_plot_clown_ref_grouper$dat %>% distinct(mods, .keep_all = T) %>%  mutate(comp="Clowfish~Grouper"),
mp_plot_clown_ref_goby$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Clowfish~Goby"),
mp_plot_clown_ref_manini$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Clowfish~Manini"),
mp_plot_clown_ref_danio$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Clowfish~Danio"),
mp_plot_grouper_ref_clown$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Grouper~Clownfish"),
mp_plot_grouper_ref_goby$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Grouper~Goby"),
mp_plot_grouper_ref_manini$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Grouper~Manini"),
mp_plot_grouper_ref_danio$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Grouper~Danio"),
mp_plot_goby_ref_clown$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Goby~Clownfish"),
mp_plot_goby_ref_grouper$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Goby~Grouper"),
mp_plot_goby_ref_manini$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Goby~Manini"),
mp_plot_goby_ref_danio$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Goby~Danio"),
mp_plot_manini_ref_clown$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Manini~Clownfish"),
mp_plot_manini_ref_grouper$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Manini~Grouper"),
mp_plot_manini_ref_goby$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Manini~Goby"),
mp_plot_manini_ref_danio$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Manini~Danio"),
mp_plot_danio_ref_clown$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Danio~Clownfish"),
mp_plot_danio_ref_grouper$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Danio~Grouper"),
mp_plot_danio_ref_goby$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Danio~Goby"),
mp_plot_danio_ref_manini$dat %>% distinct(mods, .keep_all = T) %>% mutate(comp="Danio~Manini")
) %>% 
  dplyr::count(pres, comp) %>% 
  mutate(comp=reorder(comp, -n)) %>%  
  ggplot(aes(y=comp, x=n))+
    facet_wrap(~pres)+
  geom_col(aes(fill=pres), color="grey20", linewidth=0.2, position = "stack")+
    geom_text(aes(label=n, x=n-1.2), color="white", size=3)+
  scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
  labs(x="Comparisons", y="Number of modules")+
  theme_bw()+
  theme(axis.text.y = element_text(angle=0,size=8,hjust = 1, vjust = 0.5),
        axis.text.x = element_text(size=8),
        strip.background = element_rect(fill = "grey95"))
```

The following plots show the Jaccard indices for all the module comparisons with the significant higher than expected overlaps marked in red. I pick the module pairs with the highest Jaccard similarity and classify them as the conserved ones. Those are highlighted with black outline. The preservation classification is on the x and y axis. You can see that most homologous modules are usually highly preserved. 

#### Clownfish and goby

```{r 06_homologous_modules_and_gene_lists-chunk-004, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(clown_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(goby_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = clown_orth_net$moduleColors, 
                                   net2 = goby_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.goby=reorder(c2,-jaccard_index)) %>% 
  mutate(col.clown=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_clown_ref_goby$dat %>% dplyr::rename(col.clown=mods),
          membership_stats, by = "col.clown",relationship = "many-to-many") %>% 
  dplyr::rename(clown.pres=pres, stages.clown=stages, mod.z.clown=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_goby_ref_clown$dat %>% dplyr::rename(col.goby=mods),
          membership_stats, by = "col.goby",relationship = "many-to-many") %>% 
  dplyr::rename(goby.pres=pres, stages.goby=stages, mod.z.goby=mod.z) ->membership_stats

membership_stats %>% dplyr::select(c(col.clown, col.goby, jaccard_index, padj, clown.pres, goby.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index))->membership_stats2

full_join(membership_stats %>% dplyr::select(c(col.clown, col.goby, jaccard_index, padj, clown.pres, goby.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.clown,col.goby, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.clown,n = 2,) %>% dplyr::select(col.clown,col.goby,homo),by = c("col.clown","col.goby")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.goby, y=col.clown))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  scale_y_discrete(position = "right") +
  facet_grid(clown.pres~goby.pres,space = "free",scales = "free")+
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.clown, col.goby, jaccard_index, padj, clown.pres, goby.pres,phase.x)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(x=col.goby,y=1))+
    geom_tile(aes(fill=goby.pres))+
    facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="Goby modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.clown, col.goby, jaccard_index, padj, clown.pres, goby.pres,phase.y)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(y=col.clown,x=1))+
    facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=clown.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Clownfish modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.clown)
  membership_stats %>% 
  ggplot(aes(x = stages.clown,y = col.clown))+
  facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.clown), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.clown(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Clownfish stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.goby)
  membership_stats %>% 
  ggplot(aes(y = stages.goby,x = col.goby))+
  facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.goby), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.goby(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="Goby stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
  
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_clown_goby
wrapped_plot_clown_goby
```

#### Clownfish and grouper

```{r 06_homologous_modules_and_gene_lists-chunk-005, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(clown_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(grouper_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = clown_orth_net$moduleColors, 
                                   net2 = grouper_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.grouper=reorder(c2,-jaccard_index)) %>% 
  mutate(col.clown=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_clown_ref_grouper$dat %>% dplyr::rename(col.clown=mods),
          membership_stats, by = "col.clown",relationship = "many-to-many") %>% 
  dplyr::rename(clown.pres=pres, stages.clown=stages, mod.z.clown=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_grouper_ref_clown$dat %>% dplyr::rename(col.grouper=mods),
          membership_stats, by = "col.grouper",relationship = "many-to-many") %>% 
  dplyr::rename(grouper.pres=pres, stages.grouper=stages, mod.z.grouper=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.clown, col.grouper, jaccard_index, padj, clown.pres, grouper.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index))->membership_stats2

full_join(membership_stats %>% dplyr::select(c(col.clown, col.grouper, jaccard_index, padj, clown.pres, grouper.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.clown,col.grouper, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.grouper, n=2) %>% dplyr::select(col.clown,col.grouper,homo),by = c("col.clown","col.grouper")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.grouper, y=col.clown))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  scale_y_discrete(position = "right") +
  facet_grid(clown.pres~grouper.pres,space = "free",scales = "free")+
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.clown, col.grouper, jaccard_index, padj, clown.pres, grouper.pres,phase.x)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(x=col.grouper,y=1))+
    geom_tile(aes(fill=grouper.pres))+
    facet_grid(cols = vars(grouper.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="Grouper modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.clown, col.grouper, jaccard_index, padj, clown.pres, grouper.pres,phase.y)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(y=col.clown,x=1))+
    facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=clown.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Clownfish modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.clown)
  membership_stats %>% 
  ggplot(aes(x = stages.clown,y = col.clown))+
  facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.clown), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.clown(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Clownfish stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.grouper)
  membership_stats %>% 
  ggplot(aes(y = stages.grouper,x = col.grouper))+
  facet_grid(cols = vars(grouper.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.grouper), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.grouper(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="Grouper stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
  
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_clown_grouper
wrapped_plot_clown_grouper
```

#### Clownfish and manini

```{r 06_homologous_modules_and_gene_lists-chunk-006, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(clown_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(manini_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = clown_orth_net$moduleColors, 
                                   net2 = manini_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.manini=reorder(c2,-jaccard_index)) %>% 
  mutate(col.clown=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_clown_ref_manini$dat %>% dplyr::rename(col.clown=mods),
          membership_stats, by = "col.clown",relationship = "many-to-many") %>% 
  dplyr::rename(clown.pres=pres, stages.clown=stages, mod.z.clown=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_manini_ref_clown$dat %>% dplyr::rename(col.manini=mods),
          membership_stats, by = "col.manini",relationship = "many-to-many") %>% 
  dplyr::rename(manini.pres=pres, stages.manini=stages, mod.z.manini=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.clown, col.manini, jaccard_index, padj, clown.pres, manini.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index))->membership_stats2

 full_join(membership_stats %>% dplyr::select(c(col.clown, col.manini, jaccard_index, padj, clown.pres, manini.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.clown,col.manini, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.clown, n=2) %>% dplyr::select(col.clown,col.manini,homo),by = c("col.clown","col.manini")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.manini, y=col.clown))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  scale_y_discrete(position = "right") +
  facet_grid(clown.pres~manini.pres,space = "free",scales = "free")+
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.clown, col.manini, jaccard_index, padj, clown.pres, manini.pres,phase.x)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(x=col.manini,y=1))+
    geom_tile(aes(fill=manini.pres))+
    facet_grid(cols = vars(manini.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="manini modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.clown, col.manini, jaccard_index, padj, clown.pres, manini.pres,phase.y)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(y=col.clown,x=1))+
    facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=clown.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Clownfish modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.clown)
  membership_stats %>% 
  ggplot(aes(x = stages.clown,y = col.clown))+
  facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.clown), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.clown(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Clownfish stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.manini)
  membership_stats %>% 
  ggplot(aes(y = stages.manini,x = col.manini))+
  facet_grid(cols = vars(manini.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.manini), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.manini(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="manini stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_clown_manini
wrapped_plot_clown_manini
```

#### Clownfish and danio

```{r 06_homologous_modules_and_gene_lists-chunk-007, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(clown_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(danio_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = clown_orth_net$moduleColors, 
                                   net2 = danio_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.danio=reorder(c2,-jaccard_index)) %>% 
  mutate(col.clown=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_clown_ref_danio$dat %>% dplyr::rename(col.clown=mods),
          membership_stats, by = "col.clown",relationship = "many-to-many") %>% 
  dplyr::rename(clown.pres=pres, stages.clown=stages, mod.z.clown=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_danio_ref_clown$dat %>% dplyr::rename(col.danio=mods),
          membership_stats, by = "col.danio",relationship = "many-to-many") %>% 
  dplyr::rename(danio.pres=pres, stages.danio=stages, mod.z.danio=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.clown, col.danio, jaccard_index, padj, clown.pres, danio.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index))->membership_stats2

 full_join(membership_stats %>% dplyr::select(c(col.clown, col.danio, jaccard_index, padj, clown.pres, danio.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.clown,col.danio, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.clown, n=2) %>% dplyr::select(col.clown,col.danio,homo),by = c("col.clown","col.danio")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.danio, y=col.clown))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  scale_y_discrete(position = "right") +
  facet_grid(clown.pres~danio.pres,space = "free",scales = "free")+
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.clown, col.danio, jaccard_index, padj, clown.pres, danio.pres,phase.x)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(x=col.danio,y=1))+
    geom_tile(aes(fill=danio.pres))+
    facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="danio modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.clown, col.danio, jaccard_index, padj, clown.pres, danio.pres,phase.y)) %>% mutate(col.clown=reorder(col.clown,-jaccard_index)) %>% 
    ggplot(aes(y=col.clown,x=1))+
    facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=clown.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Clownfish modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.clown)
  membership_stats %>% 
  ggplot(aes(x = stages.clown,y = col.clown))+
  facet_grid(rows = vars(clown.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.clown), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.clown(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Clownfish stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.danio)
  membership_stats %>% 
  ggplot(aes(y = stages.danio,x = col.danio))+
  facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.danio), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.danio(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="danio stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_clown_danio
wrapped_plot_clown_danio
```

#### Grouper and manini

```{r 06_homologous_modules_and_gene_lists-chunk-008, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(grouper_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(manini_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = grouper_orth_net$moduleColors, 
                                   net2 = manini_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.manini=reorder(c2,-jaccard_index)) %>% 
  mutate(col.grouper=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_grouper_ref_manini$dat %>% dplyr::rename(col.grouper=mods),
          membership_stats, by = "col.grouper",relationship = "many-to-many") %>% 
  dplyr::rename(grouper.pres=pres, stages.grouper=stages, mod.z.grouper=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_manini_ref_grouper$dat %>% dplyr::rename(col.manini=mods),
          membership_stats, by = "col.manini",relationship = "many-to-many") %>% 
  dplyr::rename(manini.pres=pres, stages.manini=stages, mod.z.manini=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.grouper, col.manini, jaccard_index, padj, grouper.pres, manini.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.grouper=reorder(col.grouper,-jaccard_index))->membership_stats2


 full_join(membership_stats %>% dplyr::select(c(col.grouper, col.manini, jaccard_index, padj, grouper.pres, manini.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.grouper,col.manini, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.grouper, n=2) %>% dplyr::select(col.grouper,col.manini,homo),by = c("col.grouper","col.manini")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.manini, y=col.grouper))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(grouper.pres~manini.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1
  
  membership_stats %>% dplyr::select(c(col.grouper, col.manini, jaccard_index, padj, grouper.pres, manini.pres,phase.x)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(x=col.manini,y=1))+
    geom_tile(aes(fill=manini.pres))+
    facet_grid(cols = vars(manini.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="Manini modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.grouper, col.manini, jaccard_index, padj, grouper.pres, manini.pres,phase.y)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(y=col.grouper,x=1))+
    facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=grouper.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Grouper modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.grouper)
  membership_stats %>% 
  ggplot(aes(x = stages.grouper,y = col.grouper))+
  facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.grouper), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.grouper(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Grouper stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.manini)
  membership_stats %>% 
  ggplot(aes(y = stages.manini,x = col.manini))+
  facet_grid(cols = vars(manini.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.manini), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.manini(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="Manini stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_grouper_manini
wrapped_plot_grouper_manini
```

#### Grouper and goby

```{r 06_homologous_modules_and_gene_lists-chunk-009, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(grouper_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(goby_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = grouper_orth_net$moduleColors, 
                                   net2 = goby_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.goby=reorder(c2,-jaccard_index)) %>% 
  mutate(col.grouper=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_grouper_ref_goby$dat %>% dplyr::rename(col.grouper=mods),
          membership_stats, by = "col.grouper",relationship = "many-to-many") %>% 
  dplyr::rename(grouper.pres=pres, stages.grouper=stages, mod.z.grouper=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_goby_ref_grouper$dat %>% dplyr::rename(col.goby=mods),
          membership_stats, by = "col.goby",relationship = "many-to-many") %>% 
  dplyr::rename(goby.pres=pres, stages.goby=stages, mod.z.goby=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.grouper, col.goby, jaccard_index, padj, grouper.pres, goby.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.grouper=reorder(col.grouper,-jaccard_index))->membership_stats2


 full_join(membership_stats %>% dplyr::select(c(col.grouper, col.goby, jaccard_index, padj, grouper.pres, goby.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.grouper,col.goby, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.grouper, n=2) %>% dplyr::select(col.grouper,col.goby,homo),by = c("col.grouper","col.goby")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.goby, y=col.grouper))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(grouper.pres~goby.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.grouper, col.goby, jaccard_index, padj, grouper.pres, goby.pres,phase.x)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(x=col.goby,y=1))+
    geom_tile(aes(fill=goby.pres))+
    facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="Goby modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.grouper, col.goby, jaccard_index, padj, grouper.pres, goby.pres,phase.y)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(y=col.grouper,x=1))+
    facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=grouper.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Grouper modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.grouper)
  membership_stats %>% 
  ggplot(aes(x = stages.grouper,y = col.grouper))+
  facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.grouper), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.grouper(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Grouper stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.goby)
  membership_stats %>% 
  ggplot(aes(y = stages.goby,x = col.goby))+
  facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.goby), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.goby(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="Goby stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_grouper_goby
wrapped_plot_grouper_goby
```

#### Grouper and danio

```{r 06_homologous_modules_and_gene_lists-chunk-010, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

expand_grid(c1=(grouper_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(danio_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = grouper_orth_net$moduleColors, 
                                   net2 = danio_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.danio=reorder(c2,-jaccard_index)) %>% 
  mutate(col.grouper=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_grouper_ref_danio$dat %>% dplyr::rename(col.grouper=mods),
          membership_stats, by = "col.grouper",relationship = "many-to-many") %>% 
  dplyr::rename(grouper.pres=pres, stages.grouper=stages, mod.z.grouper=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_danio_ref_grouper$dat %>% dplyr::rename(col.danio=mods),
          membership_stats, by = "col.danio",relationship = "many-to-many") %>% 
  dplyr::rename(danio.pres=pres, stages.danio=stages, mod.z.danio=mod.z) ->membership_stats


membership_stats %>% dplyr::select(c(col.grouper, col.danio, jaccard_index, padj, grouper.pres, danio.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.grouper=reorder(col.grouper,-jaccard_index))->membership_stats2


 full_join(membership_stats %>% dplyr::select(c(col.grouper, col.danio, jaccard_index, padj, grouper.pres, danio.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.grouper,col.danio, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.grouper, n=2) %>% dplyr::select(col.grouper,col.danio,homo),by = c("col.grouper","col.danio")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.danio, y=col.grouper))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(grouper.pres~danio.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("black","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1

  
  membership_stats %>% dplyr::select(c(col.grouper, col.danio, jaccard_index, padj, grouper.pres, danio.pres,phase.x)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(x=col.danio,y=1))+
    geom_tile(aes(fill=danio.pres))+
    facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="danio modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  membership_stats %>% dplyr::select(c(col.grouper, col.danio, jaccard_index, padj, grouper.pres, danio.pres,phase.y)) %>% mutate(col.grouper=reorder(col.grouper,-jaccard_index)) %>% 
    ggplot(aes(y=col.grouper,x=1))+
    facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=grouper.pres))+
    scale_y_discrete(position = "right") +
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Grouper modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.grouper)
  membership_stats %>% 
  ggplot(aes(x = stages.grouper,y = col.grouper))+
  facet_grid(rows = vars(grouper.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.grouper), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.grouper(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Grouper stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.danio)
  membership_stats %>% 
  ggplot(aes(y = stages.danio,x = col.danio))+
  facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.danio), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.danio(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="danio stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_grouper_danio
wrapped_plot_grouper_danio
```

#### Manini and goby

```{r 06_homologous_modules_and_gene_lists-chunk-011, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385


expand_grid(c1=(manini_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(goby_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = manini_orth_net$moduleColors, 
                                   net2 = goby_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.goby=reorder(c2,-jaccard_index)) %>% 
  mutate(col.manini=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_manini_ref_goby$dat %>% dplyr::rename(col.manini=mods),
          membership_stats, by = "col.manini",relationship = "many-to-many") %>% 
  dplyr::rename(manini.pres=pres, stages.manini=stages, mod.z.manini=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_goby_ref_manini$dat %>% dplyr::rename(col.goby=mods),
          membership_stats, by = "col.goby",relationship = "many-to-many") %>% 
  dplyr::rename(goby.pres=pres, stages.goby=stages, mod.z.goby=mod.z) ->membership_stats

membership_stats %>% dplyr::select(c(col.manini, col.goby, jaccard_index, padj, manini.pres, goby.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.manini=reorder(col.manini,-jaccard_index))->membership_stats2



 full_join(membership_stats %>% dplyr::select(c(col.manini, col.goby, jaccard_index, padj, manini.pres, goby.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.manini=reorder(col.manini,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.manini,col.goby, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.goby, n=2) %>% dplyr::select(col.manini,col.goby,homo),by = c("col.manini","col.goby")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.goby, y=col.manini))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(manini.pres~goby.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("grey15","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1


  membership_stats %>% dplyr::select(c(col.manini, col.goby, jaccard_index, padj, manini.pres, goby.pres,phase.x))  %>% mutate(col.manini=reorder(col.manini,-jaccard_index)) %>% 
    ggplot(aes(x=col.goby,y=1))+
    facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=goby.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="Goby modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  
  
  membership_stats %>% dplyr::select(c(col.manini, col.goby, jaccard_index, padj, manini.pres, goby.pres,phase.y)) %>% mutate(col.manini=reorder(col.manini,-jaccard_index)) %>% 
    ggplot(aes(y=col.manini,x=1))+
    facet_grid(rows = vars(manini.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=manini.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    scale_y_discrete(position = "right") +
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Manini modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.manini)
  membership_stats %>% 
  ggplot(aes(x = stages.manini,y = col.manini))+
  facet_grid(rows = vars(manini.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.manini), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.manini(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Manini stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.goby)
  membership_stats %>% 
  ggplot(aes(y = stages.goby,x = col.goby))+
  facet_grid(cols = vars(goby.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.goby), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.goby(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="Goby stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
  
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_manini_goby
wrapped_plot_manini_goby
```

#### Manini and danio

```{r 06_homologous_modules_and_gene_lists-chunk-012, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385


expand_grid(c1=(manini_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(danio_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = manini_orth_net$moduleColors, 
                                   net2 = danio_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.danio=reorder(c2,-jaccard_index)) %>% 
  mutate(col.manini=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_manini_ref_danio$dat %>% dplyr::rename(col.manini=mods),
          membership_stats, by = "col.manini",relationship = "many-to-many") %>% 
  dplyr::rename(manini.pres=pres, stages.manini=stages, mod.z.manini=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_danio_ref_manini$dat %>% dplyr::rename(col.danio=mods),
          membership_stats, by = "col.danio",relationship = "many-to-many") %>% 
  dplyr::rename(danio.pres=pres, stages.danio=stages, mod.z.danio=mod.z) ->membership_stats

membership_stats %>% dplyr::select(c(col.manini, col.danio, jaccard_index, padj, manini.pres, danio.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.manini=reorder(col.manini,-jaccard_index))->membership_stats2



 full_join(membership_stats %>% dplyr::select(c(col.manini, col.danio, jaccard_index, padj, manini.pres, danio.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.manini=reorder(col.manini,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.manini,col.danio, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.danio, n=2) %>% dplyr::select(col.manini,col.danio,homo),by = c("col.manini","col.danio")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.danio, y=col.manini))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(manini.pres~danio.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("grey15","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1


  membership_stats %>% dplyr::select(c(col.manini, col.danio, jaccard_index, padj, manini.pres, danio.pres,phase.x))  %>% mutate(col.manini=reorder(col.manini,-jaccard_index)) %>% 
    ggplot(aes(x=col.danio,y=1))+
    facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=danio.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="danio modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  
  
  membership_stats %>% dplyr::select(c(col.manini, col.danio, jaccard_index, padj, manini.pres, danio.pres,phase.y)) %>% mutate(col.manini=reorder(col.manini,-jaccard_index)) %>% 
    ggplot(aes(y=col.manini,x=1))+
    facet_grid(rows = vars(manini.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=manini.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    scale_y_discrete(position = "right") +
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="Manini modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.manini)
  membership_stats %>% 
  ggplot(aes(x = stages.manini,y = col.manini))+
  facet_grid(rows = vars(manini.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.manini), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.manini(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="Manini stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.danio)
  membership_stats %>% 
  ggplot(aes(y = stages.danio,x = col.danio))+
  facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.danio), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.danio(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="danio stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
  
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_manini_danio
wrapped_plot_manini_danio
```

#### Goby and danio

```{r 06_homologous_modules_and_gene_lists-chunk-013, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385


expand_grid(c1=(goby_orth_net$connectivity %>% distinct(module) %>% pull(module)), 
            c2=(danio_orth_net$connectivity %>% distinct(module) %>% pull(module)))->jac_input

# Run the function with the ability to specify net1 and net2
purrr::map2(.x = jac_input$c1, 
            .y = jac_input$c2,  
            ~ get_jaccard_estimate(.x, .y, 
                                   net1 = goby_orth_net$moduleColors, 
                                   net2 = danio_orth_net$moduleColors)) %>% list_rbind() %>% 
  arrange(desc(jaccard_index))->membership_stats

#Reorder colums and adjust the pvalues
membership_stats %>% mutate(col.danio=reorder(c2,-jaccard_index)) %>% 
  mutate(col.goby=reorder(c1,-jaccard_index)) %>% 
  mutate(padj=p.adjust(membership_stats$f.test.pval,"BH"))->membership_stats

#Join with the heatmap data
full_join(mp_plot_goby_ref_danio$dat %>% dplyr::rename(col.goby=mods),
          membership_stats, by = "col.goby",relationship = "many-to-many") %>% 
  dplyr::rename(goby.pres=pres, stages.goby=stages, mod.z.goby=mod.z)->membership_stats
#Join with the heatmap data
full_join(mp_plot_danio_ref_goby$dat %>% dplyr::rename(col.danio=mods),
          membership_stats, by = "col.danio",relationship = "many-to-many") %>% 
  dplyr::rename(danio.pres=pres, stages.danio=stages, mod.z.danio=mod.z) ->membership_stats

membership_stats %>% dplyr::select(c(col.goby, col.danio, jaccard_index, padj, goby.pres, danio.pres)) %>% 
  mutate(sig_ovelap=case_when(
  padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>%  mutate(col.goby=reorder(col.goby,-jaccard_index))->membership_stats2



 full_join(membership_stats %>% dplyr::select(c(col.goby, col.danio, jaccard_index, padj, goby.pres, danio.pres)) %>%
             mutate(sig_ovelap=case_when(
               padj < 0.05 ~ "yes", padj > 0.05 ~ "no")) %>% mutate(col.goby=reorder(col.goby,-jaccard_index)),
           membership_stats2 %>% filter(sig_ovelap == "yes") %>% 
             mutate(homo=case_when(
               jaccard_index >= quantile(membership_stats$jaccard_index,0.75) & sig_ovelap == "yes" ~ "homologous",
               .default = "non-homologous")) %>% 
     distinct(col.goby,col.danio, .keep_all = T) %>% 
   slice_max(order_by = jaccard_index,by = col.goby, n=2) %>% dplyr::select(col.goby,col.danio,homo),by = c("col.goby","col.danio")) %>%
   replace_na(list(homo="non-homologous"))->membership_stats2
  
membership_stats2 %>%  
  ggplot(aes(x=col.danio, y=col.goby))+
  geom_tile(aes(fill=jaccard_index, color=homo, width=0.8, height=0.8), size=0.3)+
  facet_grid(goby.pres~danio.pres,space = "free",scales = "free")+
  scale_y_discrete(position = "right") +
  labs(x=NULL, y=NULL)+
  scale_fill_gradientn(colours = RColorBrewer::brewer.pal(9,"Oranges"),limits=c(0,0.5))+
  scale_color_manual(values = c("grey15","white"))+
  ggnewscale::new_scale_color()+
  geom_point(aes(color = sig_ovelap),alpha=0.3,size=0.3,shape=8)+
  scale_color_manual(values = c("white","red3"))+
  theme_void()+
  theme(strip.text = element_blank(),
        strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = "left",
        axis.text = element_blank())->p1


  membership_stats %>% dplyr::select(c(col.goby, col.danio, jaccard_index, padj, goby.pres, danio.pres,phase.x))  %>% mutate(col.goby=reorder(col.goby,-jaccard_index)) %>% 
    ggplot(aes(x=col.danio,y=1))+
    facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=danio.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.x, y=2))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x="danio modules", y=NULL)+
    theme_minimal()+
    theme(axis.text.x = element_text(angle = -90,hjust = -0.005,vjust = 0.2),
          strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.y = element_blank(),
          legend.position = "none")->p2
  
  
  
  membership_stats %>% dplyr::select(c(col.goby, col.danio, jaccard_index, padj, goby.pres, danio.pres,phase.y)) %>% mutate(col.goby=reorder(col.goby,-jaccard_index)) %>% 
    ggplot(aes(y=col.goby,x=1))+
    facet_grid(rows = vars(goby.pres),space = "free",scales = "free")+
    geom_tile(aes(fill=goby.pres))+
    scale_fill_manual(values = c("#497BB6", "#B6497B", "#7BB649"))+
    scale_y_discrete(position = "right") +
    ggnewscale::new_scale_fill()+
    geom_tile(aes(fill=phase.y, x=0))+
    scale_fill_manual(values = c("#497", "#B64", "#7BB"))+
    labs(x=NULL, y="goby modules")+
    theme_minimal()+
    theme(strip.text = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x =  element_blank(),
          legend.position = "none")->p3
  
  qnt<-max(membership_stats$mod.z.goby)
  membership_stats %>% 
  ggplot(aes(x = stages.goby,y = col.goby))+
  facet_grid(rows = vars(goby.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.goby), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.goby(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(y=NULL, x="goby stages")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90,hjust = -0.005,vjust = 0.2),
                        strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.y = element_blank(),
                        legend.position = "top")->p4
  
  qnt<-max(membership_stats$mod.z.danio)
  membership_stats %>% 
  ggplot(aes(y = stages.danio,x = col.danio))+
  facet_grid(cols = vars(danio.pres),space = "free",scales = "free")+
  geom_tile(aes(fill = mod.z.danio), color = "grey80",) +
  scale_fill_gradientn(colors = rev(cols.danio(11)), limits = c(-qnt, qnt),
                       breaks = c(-qnt, 0, qnt), labels = c(paste0("<", round(-qnt)), "0", paste0(">", round(qnt))))+
  labs(x=NULL, y="danio stages")+
  theme_minimal()+
  theme(strip.text = element_blank(),
                        strip.background = element_blank(),
                        panel.grid = element_blank(),
                        axis.text.x = element_blank(),
                        legend.position = "bottom")->p5
  
  
  
wrap_plots(p1,p3,p2,nrow = 2,ncol = 2, heights = c(1,0.05), widths = c(1, 0.05))->wrapped_plot_goby_danio
wrapped_plot_goby_danio
```

#### Extract homologous modules

Start in sequence with the largest pairs first.

```{r 06_homologous_modules_and_gene_lists-chunk-014, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
#clown:317
#Grouper:310
#Goby:363
#Manini:385
#Zebrafish:385

inner_join(
  wrapped_plot_clown_manini[[1]][1] %>% as.data.frame() %>% filter(data.sig_ovelap == "yes") %>%
    distinct(data.col.clown, data.col.manini, .keep_all = T) %>%
    dplyr::rename(col.clown=data.col.clown, 
                  col.manini=data.col.manini, 
                  jaccard.index.clown.manini=data.jaccard_index, 
                  clown.ref.pres.manini=data.clown.pres, 
                  manini.ref.pres.clown=data.manini.pres),
  
      wrapped_plot_clown_danio[[1]][1] %>% as.data.frame() %>% filter(data.sig_ovelap == "yes") %>% distinct(data.col.clown, data.col.danio, .keep_all = T) %>% 
    dplyr::rename(col.clown=data.col.clown, 
                  col.danio=data.col.danio, 
                  jaccard.index.clown.danio=data.jaccard_index, 
                  clown.ref.pres.danio=data.clown.pres, 
                  danio.ref.pres.clown=data.danio.pres),
 by = "col.clown", relationship = "many-to-many") %>% 
  
  inner_join(
     wrapped_plot_clown_goby[[1]][1] %>% as.data.frame() %>% filter(data.sig_ovelap == "yes") %>% 
    distinct(data.col.clown, data.col.goby, .keep_all = T) %>% 
    dplyr::rename(col.clown=data.col.clown, 
                  col.goby=data.col.goby, 
                  jaccard.index.clown.goby=data.jaccard_index, 
                  clown.ref.pres.goby=data.clown.pres, 
                  goby.ref.pres.clown=data.goby.pres),
    by = "col.clown", relationship = "many-to-many") %>% 
  
  inner_join(
    wrapped_plot_clown_grouper[[1]][1] %>% as.data.frame() %>% filter(data.sig_ovelap == "yes")
    %>% distinct(data.col.clown, data.col.grouper, .keep_all = T) %>%
      dplyr::rename(col.clown=data.col.clown, 
                  col.grouper=data.col.grouper, 
                  jaccard.index.clown.grouper=data.jaccard_index, 
                  clown.ref.pres.grouper=data.clown.pres, 
                  grouper.ref.pres.clown=data.grouper.pres),
    by = "col.clown", relationship = "many-to-many") %>% 
  dplyr::select(c(col.clown,
                  col.goby,
                  col.danio,
                  col.manini,
                  col.grouper,
                  jaccard.index.clown.goby,
                  jaccard.index.clown.danio,
                  jaccard.index.clown.manini,
                  jaccard.index.clown.grouper,
                  clown.ref.pres.goby,
                  clown.ref.pres.danio,
                  clown.ref.pres.manini,
                  clown.ref.pres.grouper,
                  goby.ref.pres.clown,
                  danio.ref.pres.clown,
                  manini.ref.pres.clown,
                  grouper.ref.pres.clown))->homologous_modules

homologous_modules %>% saveRDS("./RDS/homologous_modules.rds")

```

```{r 06_homologous_modules_and_gene_lists-chunk-015, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
homologous_modules<-readRDS("./RDS/homologous_modules.rds")
```

## Extract homologous gene lists {.tabset}
Use this to extract homologous genes list. 
```{r 06_homologous_modules_and_gene_lists-chunk-017, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", eval=FALSE}
#combine all the jaccard similarities
rbind(
tibble(all_jac=homologous_modules$jaccard.index.clown.goby),
tibble(all_jac=homologous_modules$jaccard.index.clown.danio),
tibble(all_jac=homologous_modules$jaccard.index.clown.manini),
tibble(all_jac=homologous_modules$jaccard.index.clown.grouper))->all_jac

#long version of data
homologous_modules %>% pivot_longer(contains("col"), names_to = "species.col", values_to = "col") %>% 
  pivot_longer(contains("jaccard"), names_to = "jaccard.comp", values_to = "jaccard.val") %>% 
  pivot_longer(contains("pres"),names_to = "pres.comp", values_to = "pres.val")->homologous_long

#filter out the top 30% homologous module comparisons
homologous_long %>% filter(jaccard.val >= quantile(all_jac$all_jac,0.70)) %>% 
  dplyr::select(species.col, col) %>% pivot_wider(names_from = species.col, values_from = col) %>% 
  unnest(cols = c(col.goby, col.danio, col.manini, col.grouper, col.clown)) %>% 
  distinct(col.goby, col.danio, col.manini, col.grouper, col.clown)->homologous_filtered

homologous_gene_list<-function(mod){ 
  #this functions takes stable module assignments e.g. from clown and then combines all the other species and collates the data 
  #to obtain lists of genes shared between all 'homologous' modules
  #these genes can be though to represent conserved processes across species
  #annotating them shows which key processes have a high degree of co-regulation among species
  #select one column with stable annotation
  
  #homologous_filtered %>% filter(col.clown==mod)->one_col
  non_homologous_filtered %>% filter(col.clown==mod)->one_col #Use for non-homologus modules

  #get the list of 'homologus' columns in other species
  one_col %>% distinct(col.goby) %>% pull(col.goby)->goby_col_list
  one_col %>% distinct(col.danio) %>% pull(col.danio)->danio_col_list
  one_col %>% distinct(col.manini) %>% pull(col.manini)->manini_col_list
  one_col %>% distinct(col.grouper) %>% pull(col.grouper)->grouper_col_list
  
  #Here I get the genes from the above list of modules
  danio_col_get<-function(c1){danio_orth_net$connectivity %>% filter(module==c1) %>% return()}
  
  manini_col_get<-function(c1){manini_orth_net$connectivity %>% filter(module==c1) %>% return()}
  
  grouper_col_get<-function(c1){grouper_orth_net$connectivity %>% filter(module==c1) %>% return()}
  
  goby_col_get<-function(c1){goby_orth_net$connectivity %>% filter(module==c1) %>% return()}
  
  #I then combine all the genes from the list of modules above to select the genes that are present in all the modules. 
  #e.g. The orange clownfish module has significant overlap between darkgrey, tan, and green modules in zebrafish. While in manini, it has significant overlaps between darkturquoise, greenyellow, red, and green modules.
  #I take the genes from the zebrafish set and the manini set and combine them to only include genes that are present in both. I do this for the other two species.
  #The result is a list of genes that are, to an extent, co-expressed together. I say to an extent because, the same gene might not always be co-expressed together in the same module, in all species. 
  #For instance, look at the top ten genes in the common_all object. You'll see that all these genes are expressed together in the darkgrey module in zebrafish, but in manini some are expressed together in the greenyellow module, while some are expressed together in the red, or green module.  Essentially, this filtering approach captures genes that, on an average tend to be co-expressed together. This is expected considering they are different species with different developmental trajectories, but the fact that we can find a large degree of overlap between gene interactions across species highlights the presence of a common regulatory underpinning between orthologs. However, studying the deviations and specific modification of the network in each species will provide valuable information regarding the interplay of gene expression and regulatory evolution. 
  
inner_join(
    purrr::map(danio_col_list,danio_col_get) %>% list_rbind(),
    purrr::map(manini_col_list,manini_col_get) %>% list_rbind(), by = "gene", suffix = c(".danio", ".manini")) %>% 
    inner_join(purrr::map(grouper_col_list,grouper_col_get) %>% list_rbind(), by = "gene") %>% 
    inner_join(purrr::map(goby_col_list,goby_col_get) %>% list_rbind(), by = "gene", suffix = c(".grouper",".goby"))->common_all
  
  tibble(genes=common_all %>% inner_join(clown_orth_net$connectivity, by = "gene") %>% filter(module==mod)  %>% pull(gene)) %>% 
    mutate(mod=mod)%>% return()
  }

cols<-homologous_filtered %>% distinct(col.clown)
purrr::map(cols$col.clown, homologous_gene_list) %>% list_rbind() %>% distinct(genes, .keep_all = T)->homologous_genes
homologous_genes %>% distinct(mod)

homologous_genes %>% saveRDS("./RDS/homologous_genes.rds")

#Non-homologus, low preservation modules
clown_orth_net$connectivity %>% filter(!module %in% (homologous_genes %>% distinct(mod) %>% pull(mod))) %>% distinct(module)->non_homologous_mods

homologous_modules %>% filter(col.clown %in% non_homologous_mods$module) %>% pivot_longer(contains("col"), names_to = "species.col", values_to = "col") %>% 
  pivot_longer(contains("jaccard"), names_to = "jaccard.comp", values_to = "jaccard.val") %>% 
  pivot_longer(contains("pres"),names_to = "pres.comp", values_to = "pres.val")->homologous_long_non_homologus

#filter out the top 30% non-homologous module comparisons
homologous_long_non_homologus %>% filter(jaccard.val >= quantile(homologous_long_non_homologus$jaccard.val,0.70)) %>% 
  dplyr::select(species.col, col) %>% pivot_wider(names_from = species.col, values_from =
                                                    col) %>% 
  unnest(cols = c(col.goby, col.danio, col.manini, col.grouper, col.clown)) %>%
  distinct(col.goby, col.danio, col.manini, col.grouper, col.clown)->non_homologous_filtered

cols<-non_homologous_filtered %>% distinct(col.clown)
purrr::map(cols$col.clown, homologous_gene_list) %>% list_rbind() %>% distinct(genes, .keep_all = T)->non_homologous_genes
non_homologous_genes %>% distinct(mod)

non_homologous_genes %>% saveRDS("./RDS/non_homologous_genes.rds")
```

### Genes in conserved network
These are the genes in the conserved network. Then module names are based on the module assignment in clownfish.
```{r 06_homologous_modules_and_gene_lists-chunk-018, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
homologous_genes<-readRDS("./RDS/homologous_genes.rds")

homologous_genes %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "200px", height = "200px")
```

### Average connectivity of homologus genes
The genes in the consereved network on an average have higher connectivity than the other genes not in the network. Therefore, they represent hub genes.
```{r 06_homologous_modules_and_gene_lists-chunk-019, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
homologous_genes<-readRDS("./RDS/homologous_genes.rds")

#non_homologous_genes<-readRDS("./RDS/non_homologous_genes.rds")
rbind(
  clown_orth_net$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
    mutate(type="Yes"),
  clown_orth_net$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
    mutate(type="No ")) %>% mutate(sp="clownfish") %>% 
  rbind(
    rbind(
      grouper_orth_net$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="Yes"),
      grouper_orth_net$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="No")) %>% mutate(sp="grouper")) %>% 
  rbind(
    rbind(
      goby_orth_net$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="Yes"),
      goby_orth_net$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="No")) %>% mutate(sp="goby")) %>% 
  rbind(
    rbind(
      manini_orth_net$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="Yes"),
      manini_orth_net$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="No")) %>% mutate(sp="manini")) %>% 
  rbind(
    rbind(
      danio_orth_net$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="Yes"),
      danio_orth_net$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% 
        mutate(type="No")) %>% mutate(sp="zebrafish"))->connect_dat


```

```{r 06_homologous_modules_and_gene_lists-chunk-020, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", out.width="70%"}
ggarrange(
connect_dat %>% filter(sp=="clownfish") %>% 
  ggplot(aes(y=log2(degree),x=type))+
  geom_violin(alpha=0.6, color="grey35", fill="#e77515",linewidth=0.2)+
  geom_boxplot(alpha=0.5, fill="grey80", outliers = FALSE, width=0.3)+
  scale_y_continuous(limits = c(4,7.5))+
  annotate("segment", x = 1, xend = 2, y = 7.3, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 1, xend = 1, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 2, xend = 2, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("text", x = 1.5, y = 7.3, label = "***", size=5)+
  labs(x=NULL,
       y="Connectivity",
       subtitle = "Clownfish")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 10)),


connect_dat %>% filter(sp=="manini") %>% 
  ggplot(aes(y=log2(degree),x=type))+
  geom_violin(alpha=0.6, color="grey35", fill="#9acd32",linewidth=0.2)+
  geom_boxplot(alpha=0.5, fill="grey80", outliers = FALSE, width=0.3)+
  scale_y_continuous(limits = c(4,7.5))+
  annotate("segment", x = 1, xend = 2, y = 7.3, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 1, xend = 1, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 2, xend = 2, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("text", x = 1.5, y = 7.3, label = "***", size=5)+
  labs(x=NULL,
       y=NULL,
       subtitle = "Manini")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 10)),

connect_dat %>% filter(sp=="goby") %>% 
  ggplot(aes(y=log2(degree),x=type))+
  geom_violin(alpha=0.6, color="grey35", fill="#BA4566",linewidth=0.2)+
  geom_boxplot(alpha=0.5, fill="grey80", outliers = FALSE, width=0.3)+
  scale_y_continuous(limits = c(4,7.5))+
  annotate("segment", x = 1, xend = 2, y = 7.3, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 1, xend = 1, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 2, xend = 2, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("text", x = 1.5, y = 7.3, label = "**", size=5)+
  labs(x=NULL,
       y=NULL,
       subtitle = "Goby")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 10)),

connect_dat %>% filter(sp=="grouper") %>% 
  ggplot(aes(y=log2(degree),x=type))+
  geom_violin(alpha=0.6, color="grey35", fill="#D9C343",linewidth=0.2)+
  geom_boxplot(alpha=0.5, fill="grey80", outliers = FALSE, width=0.3)+
  scale_y_continuous(limits = c(4,7.5))+
  annotate("segment", x = 1, xend = 2, y = 7.3, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 1, xend = 1, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 2, xend = 2, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("text", x = 1.5, y = 7.3, label = "***", size=5)+
  labs(x=NULL,
       y="Connectivity",
       subtitle = "Grouper")+
  theme_bw()+
  theme(axis.text.x = element_text(size = 10)),

connect_dat %>% filter(sp=="grouper") %>% 
  ggplot(aes(y=log2(degree),x=type))+
  geom_violin(alpha=0.4, color="grey35", fill="#343BC2",linewidth=0.2)+
  geom_boxplot(alpha=0.5, fill="grey80", outliers = FALSE, width=0.3)+
  scale_y_continuous(limits = c(4,7.5))+
  annotate("segment", x = 1, xend = 2, y = 7.3, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 1, xend = 1, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("segment", x = 2, xend = 2, y = 7.1, yend = 7.3, linewidth=0.3) +
  annotate("text", x = 1.5, y = 7.3, label = "*", size=5)+
  labs(x=NULL,
       y=NULL,
       subtitle = "Zebrafish")+
  theme_bw()+
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10)),
ncol = 3, nrow = 2)
```

```{r 06_homologous_modules_and_gene_lists-chunk-021, eval=FALSE}

wil_test_boot<-function(dat,species){
  rbind(
    dat$connectivity %>% filter(gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% mutate(type="homologous"),
    dat$connectivity %>% filter(!gene %in% homologous_genes$genes) %>% dplyr::select(gene, degree) %>% mutate(type="other") %>% 
      slice_sample(n = 25)
  )->test_dat
  
  
  tibble(p.value=(
    wilcox.test(
      x = test_dat %>% filter(type=="homologous") %>% pull(degree),
      y = test_dat %>% filter(type=="other") %>% pull(degree),
      alternative = "greater")
    )$p.value,
         sp=paste0(species)
  ) %>% return()
}

rbind(
purrr::map(1:1000, ~wil_test_boot(dat = clown_orth_net, species = "Clownfish")) %>% 
  list_rbind(),
purrr::map(1:1000, ~wil_test_boot(dat = grouper_orth_net, species = "Grouper")) %>% 
  list_rbind(),
purrr::map(1:1000, ~wil_test_boot(dat = goby_orth_net, species = "Goby")) %>%
  list_rbind(),
purrr::map(1:1000, ~wil_test_boot(dat = manini_orth_net, species = "Manini")) %>% 
  list_rbind(),
purrr::map(1:1000, ~wil_test_boot(dat = danio_orth_net, species = "zebrafish")) %>% 
  list_rbind()
)->all_fish_wil_test_res

all_fish_wil_test_res %>% saveRDS("./RDS/all_fish_wil_test_res,rds")
```

P-values for above test
```{r 06_homologous_modules_and_gene_lists-chunk-022, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
all_fish_wil_test_res<-readRDS("./RDS/all_fish_wil_test_res,rds")

all_fish_wil_test_res %>% 
  mutate(p.adj=p.adjust(all_fish_wil_test_res$p.value, method = "BH")) %>% 
    mutate(p.adj=p.adjust(all_fish_wil_test_res$p.value, method = "BH")) %>% summarise(mean_padj=mean(p.adj), .by="sp") %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "200px", height = "200px")
```

### Preservation of conserved network modules
The modules in the conserved network had a high degree of preservation in all the species. 
```{r, fig.align='center'}
homologous_modules %>% filter(col.clown %in% homologous_genes$mod) %>% pivot_longer(c(clown.ref.pres.goby,clown.ref.pres.danio,clown.ref.pres.manini,
                                      clown.ref.pres.grouper,goby.ref.pres.clown,danio.ref.pres.clown,
                                      manini.ref.pres.clown,grouper.ref.pres.clown), 
                                    names_to = "comparisons", values_to = "module_pres") %>% 
  dplyr::count(module_pres) %>% mutate(n.per=n/sum(n)) %>% 
  ggplot(aes(x=module_pres, y=n.per, fill=module_pres))+
  geom_col(color="black", linewidth=0.2)+
  scale_fill_manual(values = c("#8C6BB1", "#2AA198", "#C97A5A"))+
  scale_y_continuous(labels = scales::percent)+
  geom_text(aes(label = paste0(round(n.per,2)*100,"%"), y=n.per-0.03), size=3, color="white")+
  labs(x="Module\npreservation", y="Percentage in\npairwise comparisons")+
  theme_bw()+
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size=8),
        legend.position = "none",
        panel.grid.major = element_line(colour = "grey95"),
        panel.grid.minor = element_line(colour = "grey95"))->homo_pres_plots

homo_pres_plots
```

### Gene copy-number of conserved network genes
Genes in the conserved network  are not comprised of gene families that vary copy-number as compared to the full ortholog set. Suggesting that the developmental network likely does not have more redundancy (purely from a genetic perspective) than other sets of gene networks. 
```{r 06_homologous_modules_and_gene_lists-chunk-023, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", fig.align='center'}

rbind(
  orth %>% filter(Orthogroup %in% homologous_genes$genes) %>% dplyr::count(Orthogroup) %>% mutate(type="Homologous"),
  orth %>% filter(Orthogroup %in% full_orths$Orthogroup & !Orthogroup %in% homologous_genes$genes) %>% 
    dplyr::count(Orthogroup)  %>% slice_sample(n=2000) %>% mutate(type="Non-homologous"))->ss_test

wilcox.test(x = ss_test %>% 
              filter(type=="Homologous") %>% pull(n) %>% log2(),
            
            y = ss_test %>% 
              filter(type=="Non-homologous") %>% 
              pull(n) %>% log2(), alternative = "two.sided")

ss_test %>%  ggplot(aes(y=log2(n), x=type, fill = type))+
  ggbeeswarm::geom_quasirandom(shape=21)+
  geom_boxplot(color="black", alpha=0.5, outliers = FALSE)+
  theme_bw()+  
  scale_fill_manual(values = c("#EA5B15","#1AAEC0"))+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())->gene_copy_number_homologous

gene_copy_number_homologous
```


## Annotate the conserved modules {.tabset}
```{r 06_homologous_modules_and_gene_lists-chunk-024, eval=FALSE}
homologous_genes<-readRDS("./RDS/homologous_genes.rds")
non_homologous_genes<-readRDS("./RDS/non_homologous_genes.rds")

homologous_genes %>% distinct(mod) %>% pull(mod)->cols
#gene_list<-tibble(genes=homologous_genes$genes) #input gene list for GO

purrr::map2(.x=cols, .y="BP",
            ~get_GOterms_homomods(module  = .x, 
                                  cat = .y,
                                  gene_set = homologous_genes),.progress = T)->homologous_mods_BP_proc
names(homologous_mods_BP_proc)<-cols
homologous_mods_BP_proc %>% saveRDS("./03.Annotations/homologous_mods_BP_proc.rds")

purrr::map2(.x=cols, .y="CC",
            ~get_GOterms_homomods(module  = .x,
                                  cat = .y,
                                  gene_set = homologous_genes),.progress = T)->homologous_mods_CC_proc
names(homologous_mods_CC_proc)<-cols
homologous_mods_CC_proc %>% saveRDS("./03.Annotations/homologous_mods_CC_proc.rds")

purrr::map2(.x=cols, .y="MF",
            ~get_GOterms_homomods(module  = .x, cat = .y,
                                  gene_set = homologous_genes),.progress = T)->homologous_mods_MF_proc
names(homologous_mods_MF_proc)<-cols
homologous_mods_MF_proc %>% saveRDS("./03.Annotations/homologous_mods_MF_proc.rds")

#Non-homologous module
#non_homologous_genes<-readRDS("./RDS/non_homologous_genes.rds")
non_homologous_genes %>% distinct(mod) %>% pull(mod)->cols

purrr::map2(.x=cols, .y="BP",
            ~get_GOterms_homomods(module = .x, 
                                  cat = .y, 
                                  gene_set = non_homologous_genes),.progress = T)->non_homologous_mods_BP_proc
names(non_homologous_mods_BP_proc)<-cols
non_homologous_mods_BP_proc %>% saveRDS("./03.Annotations/non_homologous_mods_BP_proc.rds")


purrr::map2(.x=cols, .y="CC",
            ~get_GOterms_homomods(mod = .x, 
                                  cat = .y,
                                  gene_set = non_homologous_genes),.progress = T)->non_homologous_mods_CC_proc
names(non_homologous_mods_CC_proc)<-cols
non_homologous_mods_CC_proc %>% saveRDS("./03.Annotations/non_homologous_mods_CC_proc.rds")

purrr::map2(.x=cols, .y="MF",
            ~get_GOterms_homomods(mod = .x, 
                                  cat = .y,
                                  gene_set = non_homologous_genes),.progress = T)->non_homologous_mods_MF_proc
names(non_homologous_mods_MF_proc)<-cols
non_homologous_mods_MF_proc %>% saveRDS("./03.Annotations/non_homologous_mods_MF_proc.rds")

```

```{r 06_homologous_modules_and_gene_lists-chunk-025, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
non_homologous_mods_BP_proc<-readRDS("./03.Annotations/non_homologous_mods_BP_proc.rds")
non_homologous_mods_MF_proc<-readRDS("./03.Annotations/non_homologous_mods_MF_proc.rds")
non_homologous_mods_CC_proc<-readRDS("./03.Annotations/non_homologous_mods_CC_proc.rds")
homologous_mods_BP_proc<-readRDS("./03.Annotations/homologous_mods_BP_proc.rds")
homologous_mods_MF_proc<-readRDS("./03.Annotations/homologous_mods_MF_proc.rds")
homologous_mods_CC_proc<-readRDS("./03.Annotations/homologous_mods_CC_proc.rds")

```

### Biological process GO terms

```{r 06_homologous_modules_and_gene_lists-chunk-026, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
purrr::map(homologous_mods_BP_proc,
           ~purrr::pluck(.x) %>% head(10)
) %>% list_rbind() %>%  
  kableExtra::kbl() %>% kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "600px", height = "500px")
```

### Molecular function GO terms

```{r 06_homologous_modules_and_gene_lists-chunk-027, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
purrr::map(homologous_mods_MF_proc,
           ~purrr::pluck(.x) %>% head(10)
) %>% list_rbind() %>%  
  kableExtra::kbl() %>% kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "600px", height = "500px")
```

### Cellular compartmentGO terms

```{r 06_homologous_modules_and_gene_lists-chunk-028, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
purrr::map(homologous_mods_CC_proc,
           ~purrr::pluck(.x) %>% head(10)
) %>% list_rbind() %>%  
  kableExtra::kbl() %>% kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "600px", height = "500px")
```

### Conserved modules GO plots
Use this to make the GO term plots in figure S4.
```{r 06_homologous_modules_and_gene_lists-chunk-016, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/", eval=FALSE}
homologous_modules %>% dplyr::select(col.clown, col.goby, col.danio, col.manini, col.grouper) %>% distinct(col.clown, .keep_all = TRUE) %>% filter(col.clown %in% unique(as.character((homologous_mods_BP_proc %>% list_rbind())$mod)))->mods_combs
#mods_combs %>% 
#  filter(col.clown %in% 
#           (cafe_genefamily_outs %>% filter(is_sig=="y") %>% pull(mod)))->mods_combs

  
safe_homo <- purrr::safely(homo_mods_lines, otherwise = NULL, quiet = TRUE)

  purrr::pmap(list(as.character(mods_combs$col.clown),
                   as.character(mods_combs$col.manini),
                   as.character(mods_combs$col.goby),
                   as.character(mods_combs$col.grouper),
                   as.character(mods_combs$col.danio)),
              ~safe_homo(mod.clown = ..1,
                                    mod.manini = ..2,
                                    mod.goby = ..3,
                                    mod.grouper = ..4,
                                    mod.danio = ..5,
                               GO_dat = homologous_mods_BP_proc %>% list_rbind() %>% 
                           filter(mod %in% mods_combs$col.clown))) %>%
  purrr::map("result") %>% purrr::compact()->homo_lines
  
  

names(homo_lines)<-homologous_mods_BP_proc %>% list_rbind() %>% 
    filter(mod %in% mods_combs$col.clown) %>% pull(mod) %>% as.character() %>% unique()
  
```

### Module annotation
These are the annotations of the modules. 
```{r 06_homologous_modules_and_gene_lists-chunk-029, cache=TRUE, cache.path="cache/06_homologous_modules_and_gene_lists/"}
homologous_genes %>% distinct(mod) %>% mutate(annot=
                                                c("RNA processing 1",
                                                  "Aerobic respiration",
                                                  "Translation",
                                                  "Neuron migration and placode development",
                                                  "Synaptic signalling 1",
                                                  "Peroxisome process",
                                                  "Synaptic signalling 2",
                                                  "Cell cycle process",
                                                  "DNA replication",
                                                  "Protein catabolism",
                                                  "Ribosome related",
                                                  "RNA processing 2",
                                                  "Translation 2",
                                                  "Extracellular matrix and cartilage development 1",
                                                  "Extracellular matrix and cartilage development 2",
                                                  "Muscle system",
                                                  "Immune system",
                                                  "Nutrient absorption",
                                                  "Brush border epithelium development",
                                                  "Blood related",
                                                  "Neural plate formation",
                                                  "Eye development","Protein folding",
                                                  "Hormone response",
                                                  "Sterol synthesis"))->module_annot

module_annot %>%  
  kableExtra::kbl() %>% kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "600px", height = "500px")
```
